### 2017-06-28 Paper Drafts/Final/finalDraft.tex
Fixing final typos

\author[J.P. Meagher et al.]{J.P. Meagher\footnote{J.P Meagher would like to thank the EPSRC for funding this work, and also acknowledge the support of the Alan Turing Institute and Gaelic Players Association.}, T. Damoulas\footnote{The University of Warwick and The Alan Turing Institute}, K.E. Jones\footnote{Centre for Biodiversity and Environment Research, University College London}, and M. Girolami\footnote{Imperial College London and The Alan Turing Institute}\\}
%\index[aindx]{Author, F.} % or \aindx{Author, F.}
%\index[aindx]{Author, S.} % or \aindx{Author, S.}

@@

Monitoring bat populations provides useful information, but an understanding the orders evolutionary history is required to identify the cause and effect of any changes observed. The echolocation call structure, which reflects a bats diet and habitat \cite{aldridge1987morphology}, is a key aspect of this evolutionary history. Reconstructing ancestral traits \cite{joy2016ancestral} relies on a statistical comparative analysis incorporating extant species and fossil records \cite{felsenstein2004inferring}. However, the fossil record is of limited use in inferring ancestral echolocation calls in bats. Therefore, statistical data science techniques may shed some light on this topic.

Previous studies of bat echolocation calls for both classification \cite{walters2012continental} and ancestral reconstruction \cite{collen2012evolution} analysed features extracted from the call spectrogram. These call features relied upon domain knowledge to ensure they were sensibly selected and applied. More recently, general techniques for the classification of acoustic signals have been developed \cite{stathopoulos2014bat} \cite{damoulas2010bayesian}. General techniques for the ancestral reconstruction of function-valued traits have also been proposed \cite{group2012phylogenetic}. Jones \& Moriarty \cite{jones2013evolutionary} extend Gaussian Process Regression \cite{rasmussen2006gaussian} to model the evolution of function-valued traits \cite{meyer2005up} over a phylogeny, a method which was demonstrated for synthetic data by Hajipantelis et al \cite{hadjipantelis2013function}. This current research investigates these techniques in the context of the bat echolocation calls.

@@

The problem of obtaining estimators \(\hat{\phi}_F\) and \(\hat{X}_{\mathbf{T}}\) is dealt with by Hajipantelis et al \cite{hadjipantelis2013function}. \(\hat{\phi}_F\) is obtained by Independent Components Analysis, as described by Blaschke \& Wiscott \cite{blaschke2004cubica} after using a resampling procedure to obtain stable principal components for the observed traits. Given \(\hat{\phi}_F\), the estimated matrix of mixing coefficients is \(\hat{X}_{\mathbf{T}} = \mathcal{E} (\hat{\phi}_F^{\mathsf{T}})^{-1}\).

@@

Post processed echolocation call data accompanying Stathopoulos et al. \cite{stathopoulos2017bat} was used in this analysis. Live bats were caught, identified, and recorded in at a sampling frequency of 500 kHz. 
In total the dataset consists of 22 species from five families, 449 individual bats and 1816 individual echolocation call recordings. The distribution of these call recordings across species is summarised in Table \ref{tab::dataset}.

>>>>

\author[J.P. Meagher \textit{et al.}]{J.P. Meagher\footnote{J.P Meagher would like to thank the EPSRC for funding this work, and also acknowledge the support of the Alan Turing Institute and Gaelic Players Association.}, T. Damoulas\footnote{The University of Warwick and The Alan Turing Institute}, K.E. Jones\footnote{Centre for Biodiversity and Environment Research, University College London}, and M. Girolami\footnote{Imperial College London and The Alan Turing Institute}\\}
%\index[aindx]{Author, F.} % or \aindx{Author, F.}
%\index[aindx]{Author, S.} % or \aindx{Author, S.}

@@

Monitoring bat populations provides useful information, but an understanding of the evolutionary history is required to identify the cause and effect of any changes observed. The echolocation call structure, which reflects a bats diet and habitat \cite{aldridge1987morphology}, is a key aspect of this evolutionary history. Reconstructing ancestral traits \cite{joy2016ancestral} relies on a statistical comparative analysis incorporating extant species and fossil records \cite{felsenstein2004inferring}. However, the fossil record is of limited use in inferring ancestral echolocation calls in bats. Therefore, statistical data science techniques may shed some light on this topic.

Previous studies of bat echolocation calls for both classification \cite{walters2012continental} and ancestral reconstruction \cite{collen2012evolution} analysed features extracted from the call spectrogram. These call features relied upon domain knowledge to ensure they were sensibly selected and applied. More recently, general techniques for the classification of acoustic signals have been developed \cite{stathopoulos2014bat} \cite{damoulas2010bayesian}. General techniques for the ancestral reconstruction of function-valued traits have also been proposed \cite{group2012phylogenetic}. Jones \& Moriarty \cite{jones2013evolutionary} extend Gaussian Process Regression \cite{rasmussen2006gaussian} to model the evolution of function-valued traits \cite{meyer2005up} over a phylogeny, a method which was demonstrated for synthetic data by Hajipantelis \textit{et al.} \cite{hadjipantelis2013function}. This current research investigates these techniques in the context of the bat echolocation calls.

@@

The problem of obtaining estimators \(\hat{\phi}_F\) and \(\hat{X}_{\mathbf{T}}\) is dealt with by Hajipantelis \textit{et al.} \cite{hadjipantelis2013function}. \(\hat{\phi}_F\) is obtained by Independent Components Analysis, as described by Blaschke \& Wiscott \cite{blaschke2004cubica} after using a resampling procedure to obtain stable principal components for the observed traits. Given \(\hat{\phi}_F\), the estimated matrix of mixing coefficients is \(\hat{X}_{\mathbf{T}} = \mathcal{E} (\hat{\phi}_F^{\mathsf{T}})^{-1}\).

@@

Post processed echolocation call data accompanying Stathopoulos \textit{et al.} \cite{stathopoulos2017bat} was used in this analysis. Live bats were caught, identified, and recorded at a sampling frequency of 500 kHz. 
In total the dataset consists of 22 species from five families, 449 individual bats and 1816 individual echolocation call recordings. The distribution of these call recordings across species is summarised in Table \ref{tab::dataset}.
